---
title: "Left Behind"
subtitle: "Sep 2025: Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
knit: (function(input_file, encoding) { rmarkdown::render(input_file, encoding = encoding, output_file = 'index.html', output_dir = here::here('docs','studies','study-sep25')); })
---


```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r setup, include=FALSE}
library(apa)
library(see)
library(lme4)
library(lmerTest)
library(interactions)
library(jtools)
library(gridExtra)
library(kableExtra)
library(apaTables)
library(papaja)
library(rstatix)
library(knitr)
library(psych)
library(GPArotation)
library(PerformanceAnalytics)
library(gt)
library(tidytext)
library(textdata)
library(tidyverse)
library(diagram)
library(factoextra)
library(SnowballC)
library(hunspell)
library(quanteda)
library(bruceR)
library(here)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/left-behind/main/study-sep25/data/"

df_lebe <- readr::read_csv(paste0(repo_url,"df_lebe.csv"), show_col_types = FALSE)
```

```{r,include=FALSE}
df_lebe <- df_lebe %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")))

df_lebe_elg <- df_lebe %>% 
  filter(is_elg == 1)
```

# Purpose

This is a pilot study that is intended to further explore the feeling of being left behind. Specifically, we wanted to see what people intuitively write when prompted to think of the ways in which they are being left behind. Potentially, the extent to which they feel left behind, interacted with the way in which they are left behind, inform important political outcomes.

# Procedure

## Demographics

Demographic information, political ideology, and political party identification.

## Left behind

### Continuous measure

They indicated the extent to which they feel left behind on a scale of 0-100.

### Open-ended measure

They wrote, in detail, what feeling left behind means to them and what are the factors that are contributing to that feeling.

### Dimensions of feeling behind

They rated their response on a number of follow-up measures: systemic-individual; relation to government; economic-cultural; historic-recent; trajectory.

## Outcomes

Random order: (1) support for anti-democratic practices; (2) ideal candidate for an election;\
Random order: (3) anti-establishment sentiment; (4) trust in institutions.\
\
Finally, participants indicated their voting behavior in 2024.

# Eligibility

There was on bot-check with an invisible attention check.

```{r,results='asis',echo=TRUE,warning=FALSE,message=F}
eligible_n <- df_lebe %>% 
  group_by(is_elg) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  filter(is_elg == 1) %>% 
  select(n) %>% 
  unlist() %>% 
  unname()

df_lebe %>% 
  group_by(att_1) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

That gives us a total of `r eligible_n` eligible participants.\
\
Participants were recruited through Prolific and the following quota was set for political representativeness: (30% dems; 30% reps; 40% independents)

# Demographics

## Race

```{r,results='asis',echo=TRUE,warning=FALSE}
df_lebe_elg %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Gender

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  mutate(gender = ifelse(is.na(gender) | gender == "","other",gender)) %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Age

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  summarise(age_mean = round(mean(age,na.rm = T),2),
            age_sd = round(sd(age,na.rm = T),2)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Education

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```



## Income

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_lebe_elg %>% 
  ggplot(aes(x = income)) +
  geom_bar() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  coord_flip()
```

# Politics

## Ideology

Participants were asked about the extent to which they subscribe to the following ideologies on a scale of 1-7 (select NA if unfamiliar): Conservatism, Liberalism, Democratic Socialism, Libertarianism, Progressivism.

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(7,5)}
means <- df_lebe_elg %>%
  dplyr::select(PID,ideo_con:ideo_prog) %>% 
  pivot_longer(-PID,
               names_to = "ideo",
               values_to = "score") %>% 
  filter(!is.na(score)) %>% 
  group_by(ideo) %>% 
  summarise(score = mean(score)) %>% 
  ungroup()

df_lebe_elg %>%
  dplyr::select(PID,ideo_con:ideo_prog) %>% 
  pivot_longer(-PID,
               names_to = "ideo",
               values_to = "score") %>% 
  filter(!is.na(score)) %>%  
  ggplot() +
  geom_density(aes(x = score), fill = "lightblue") +
  scale_x_continuous(limits = c(1,7),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~ideo,nrow = 2)

```

## Party ID

### Initial selection

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  group_by(party_gen) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### With followups

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  group_by(party_followup) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Voting behavior: 2024

Who did you vote for in the 2024 Presidential Election?

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  group_by(vote_2024) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

# Measures

## Left behind

### Continuous

People in America come from all walks of life. Some feel left behind. We are interested in whether you feel left behind and what that means for you.\
\
**To what extent do you feel left behind?** (0 = *Not at All Left Behind* to 100 = *Extremely Left Behind*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = lebe_cont)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 10) +
  scale_x_continuous(breaks = seq(0,100,20),
                     limits = c(-10,110)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$lebe_cont,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

Interesting. Most people are under the mid-point. Ok.

### Open-ended description

[For those under 50 in the continuous measure: \
\
Although not everyone might feel overall left behind to the same extent, everyone likely does feel left behind in at least a few ways. So, regardless of your answer to the previous question...]\
\
**What does the phrase ‘feeling left behind’ mean to you in your own life? In what ways[,if any,] do you feel left behind, and why?**\
\
Please describe why you might feel left behind in as much detail as possible. There is no right or wrong answer here; just your honest thoughts about the factors that might make you feel left behind.\
\
*paste disabled\
*character range: 100-5000

```{r,echo=FALSE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  select(describe) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                position = "left") %>% 
  scroll_box(width = "100%", height = "400px")
```

### Dimensions of feeling left behind

#### Systemic-Individual\
\
Would you say the factors that make you feel left behind are more **systemic** (larger forces outside your control, like government, society, culture, or the economy) or more **individual** (your own circumstances and choices)? (1 = *Entirely Systemic* to 7 = *Entirely Individual*)\
\
*Note: I reverse-scored it here so it's more intuitive for us.

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = system_R)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$system_R,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Relation to government\
\
To what extent are the factors contributing to you feeling left behind related to the government? (1 = *Not at all related to the government* to 5 = *Extremely related to the government*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = gov)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,5,1),
                     limits = c(0,6)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$gov,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Economic-Cultural\
\
Would you say the factors that make you feel left behind are more **economic** (like income, affordability, financial security) or **cultural** (like dignity, feeling respected, feeling valued)? (1 = *Entirely Economic* to 7 = *Entirely Cultural*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = econcult)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$econcult,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### History\
\
Would you say that the factors contributing to you feeling left behind are more **historic** (i.e.,they have been present for many years) or more **recent** (i.e., they are relatively new)? (1 = *Entirely Historic* to 7 = *Entirely Recent*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = history)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$history,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Trajectory\
\
Would you say that the trajectory of the factors contributing to you feeling left behind is **negative** (i.e., things are getting worse) or **positive** (i.e., things are getting better)? (1 = *Extremely Negative* to 7 = *Extremely Positive*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = trajectory)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$trajectory,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

### Text analysis

I looped through their open-ended responses with gpt-4o to get the following: (1) left behind score; (2) labeled reasons; (3) systemic to individual; (4) government-related; (5) economic to cultural; (6) history; (7) trajectory.

#### Left behind score\
\
To what extent is this person feeling left behind?

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = leftbehind_gpt)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,5,1),
                     limits = c(0,6)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$leftbehind_gpt,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Reasons\
\
What are the factors that are making this person feel left behind?\
\
Note: I'll skip the analysis on this for now, but I think this can be useful if we want to do embeddings later on.

```{r,echo=FALSE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  select(reasons) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                position = "left") %>% 
  scroll_box(width = "100%", height = "400px")
```

#### System to individual\
\
Would you say that the factors that make this person feel left behind are more systemic (larger forces outside their control, like government, society, culture, or the economy) or more individual (their own circumstances and choice)?

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = system_to_ind_gpt)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$system_to_ind_gpt,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Government-related\
\
To what extent are the factors related to the government?

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = gov_gpt)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,5,1),
                     limits = c(0,6)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$gov_gpt,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Economic to cultural\
\
To what extent are the factors more economic (like income, affordability, financial security) or cultural (like dignity, feeling respected, feeling valued)?

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = econ_to_cult_gpt)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$econ_to_cult_gpt,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Historic\
\
To what extent are the factors more historic (i.e., they have been present for many years) or more recent (i.e., they are relatively new)? (Historic to recent)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = history_gpt)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$history_gpt,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Trajectory\
\
Is the trajectory of the factors negative (i.e., things are getting worse) or positive (i.e., things are getting better)?

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = trajectory_gpt)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$trajectory_gpt,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```


## Outcome measures

### Support for anti-democratic practices

1 = *Strongly Disagree* to 7 = *Strongly Agree*\
\
1. The [INPARTY] should reduce the number of polling stations in areas that support the [OUTPARTY].\
2. The [INPARTY] should not accept the results of elections if they lose.\
3. The [INPARTY] should ignore unfavorable court rulings.\
4. When a [INPARTY] candidate questions the outcome of an election, other [INPARTY] members should be more loyal to the [INPARTY] than to election rules or the constitution.\
5. The government should be able to censor media sources that spend more time attacking the [INPARTY] than the [OUTPARTY].

```{r,include=F}
alpha_score <- df_lebe_elg %>% 
  dplyr::select(antidem_1:antidem_5) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = antidem)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$antidem,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

### Ideal candidate

We would like to ask you about your ideal political candidate. 

#### Experience\
\
Thinking about experience with politics, where would your ideal candidate fall?\
1 = *Outsider* (no prior political office); 7 = *Insider* (many years in political office)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = elect_exp)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$elect_exp,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Change\
\
Thinking about how they would approach change, what approach would you like them to take?\
1 = *Sweeping* (bold, radical changes); 7 = *Incremental* (smaller, step-by-step changes)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = elect_change)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$elect_change,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Economic policy\
\
Thinking about their economic platform, which positions would your ideal candidate advance?\
1 = *Free Market* (low corporate taxes, deregulation); 7 = *Redistributive* (wealth tax, stronger unions)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = elect_econ)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$elect_econ,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

#### Cultural issues\
\
Thinking about cultural issues, which positions would your ideal candidate advance?\
1 = *Conservative* (pro-life, stronger police, immigration crackdown); 7 = *Progressive* (pro-choice, minority rights, inclusive immigration)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = elect_cult)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$elect_cult,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

### Anti-establishment sentiment

1 = *Strongly Disagree* to 7 = *Strongly Agree*\
\
1. The US’s economy is rigged to advantage the rich and powerful.\
2. Traditional politicians and parties don’t care about people like me.\
3. Experts in this country don’t understand the lives of people like me.\
4. Most of the time we can trust people in the government to do what is right [R].

```{r,include=F}
alpha_score <- df_lebe_elg %>% 
  dplyr::select(antiest_1:antiest_4R) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = antiest)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,7,1),
                     limits = c(0,8)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$antiest,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```

### Trust in institutions

We would now like to ask you a question about how much trust you have in certain institutions and groups. For each of the following institutions, please indicate if you trust it a lot, trust it somewhat, do not trust it very much, or do not trust it at all?\
\
1. Congress\
2. The Government\
3. The judiciary\
4. Scientists\
5. The political parties\
6. Traditional newsmedia

```{r,include=F}
alpha_score <- df_lebe_elg %>% 
  dplyr::select(trust_con:trust_news) %>% 
  psych::alpha()

alpha <- alpha_score$total[1]
```

Cronbach's alpha = `r round(alpha,2)`

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
df_lebe_elg %>% 
  ggplot(aes(x = trust)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,4,1),
                     limits = c(0,5)) +
  ylab("count") +
  geom_vline(xintercept = mean(df_lebe_elg$trust,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold"))
```
\
Broken up:\
\
```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(4,3)}
means <- df_lebe_elg %>%
  dplyr::select(PID,trust_con:trust_news) %>% 
  pivot_longer(-PID,
               names_to = "inst",
               values_to = "trust") %>% 
  filter(!is.na(trust)) %>% 
  group_by(inst) %>% 
  summarise(score = mean(trust)) %>% 
  ungroup()

df_lebe_elg %>%
  dplyr::select(PID,trust_con:trust_news) %>% 
  pivot_longer(-PID,
               names_to = "inst",
               values_to = "trust") %>% 
  filter(!is.na(trust)) %>%  
  ggplot(aes(x = trust)) +
  geom_histogram(fill = "lightblue",
                 binwidth = 1) +
  scale_x_continuous(breaks = seq(1,4,1),
                     limits = c(0,5)) +
  ylab("count") +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~inst,nrow = 2)


```

# Analysis

## Correlations

```{r,fig.align='left',echo=FALSE,warning=FALSE,message=FALSE,fig.dim=c(7,7)}
df_lebe_elg %>% 
   select(lebe_cont,system_R:trajectory,leftbehind_gpt,system_to_ind_gpt:trajectory_gpt,antidem:elect_cult) %>%
   corPlot(upper = TRUE,stars = TRUE,xsrt = 270)
```

To explore these correlations and more, see this
<a href="app/" target="_blank" rel="noopener">
  Shiny App
</a>

## Interactions

```{r,echo=TRUE,results='asis',warning=FALSE}
m1 <- lm(elect_change ~ system_R:lebe_cont,df_lebe_elg)

interact_plot(m1,
              pred = system_R,
              modx = lebe_cont,
              interval = T)
```

