---
title: "Left Behind"
subtitle: "Oct 2025A: Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
knit: (function(input_file, encoding) { rmarkdown::render(input_file, encoding = encoding, output_file = 'index.html', output_dir = here::here('docs','studies','study-oct25a')); })
---


```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r setup, include=FALSE}
library(apa)
library(see)
library(lme4)
library(lmerTest)
library(interactions)
library(jtools)
library(gridExtra)
library(kableExtra)
library(apaTables)
library(papaja)
library(rstatix)
library(knitr)
library(psych)
library(GPArotation)
library(PerformanceAnalytics)
library(gt)
library(tidytext)
library(textdata)
library(tidyverse)
library(diagram)
library(factoextra)
library(SnowballC)
library(hunspell)
library(quanteda)
library(bruceR)
library(here)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/left-behind/main/study-oct25a/data/"

df_lebe <- readr::read_csv(paste0(repo_url,"df_lebe.csv"), show_col_types = FALSE)
```

```{r,include=FALSE}
df_lebe <- df_lebe %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")))

df_lebe_elg <- df_lebe %>% 
  filter(is_elg == 1)
```

# Background

This is a pretest of local- and state-level races. We want to see which of the upcoming races (held on November 5th) features a candidate that is clearly seen as representing sweeping/radical change. To that end, we targeted residents of two states in which there are upcoming governor races (NJ and VA) and four cities in which there are upcoming mayoral races (NYC, Seattle, Minneapolis, and Cleveland).\
\
For each race, we asked the following about the top two polling candidates: (1) approach to change; (2) positions on cultural issues; and (3) positions on economic issues.\
\
We then asked about voting intention and political affiliation.

# Eligibility

We used prolific to target NJ and VA residents; and Connect to target NYC, Seattle, Minneapolis, and Cleveland residents. Eligible participants are those who are indeed residents of one of these places; ineligible participants were routed out after this initial prescreen.

```{r,results='asis',echo=TRUE,warning=FALSE,message=F}
eligible_n <- df_lebe %>% 
  group_by(is_elg) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  filter(is_elg == 1) %>% 
  select(n) %>% 
  unlist() %>% 
  unname()

df_lebe %>% 
  group_by(is_elg) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

That gives us a total of `r eligible_n` eligible participants.

# Races

```{r,results='asis',echo=TRUE,warning=FALSE}
df_lebe_elg %>% 
  group_by(PLACENAME) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

# Demographics

## Race

```{r,results='asis',echo=TRUE,warning=FALSE}
df_lebe_elg %>% 
  group_by(race) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Gender

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  mutate(gender = ifelse(is.na(gender) | gender == "","other",gender)) %>% 
  group_by(gender) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Age

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  summarise(age_mean = round(mean(age,na.rm = T),2),
            age_sd = round(sd(age,na.rm = T),2)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Education

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  group_by(edu) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Income

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(5,3)}
df_lebe_elg %>% 
  ggplot(aes(x = income)) +
  geom_bar() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank()) +
  coord_flip()
```

# Political profile

## Ideology

Please indicate your general political ideology (1 = *Extremely Liberal* to 7 = *Extremely Consevative*)

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(7,5)}
df_lebe_elg %>%
  ggplot() +
  geom_histogram(aes(x = ideo), fill = "lightblue",color= NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(xintercept = mean(df_lebe_elg$ideo,na.rm = T),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold"))

```

## Party ID

### Initial selection

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  group_by(party_gen) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### With followups

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  group_by(party_followup) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```


# Perception of Candidates

## New Jersey

### Approach to change

For each candidate, would you describe them as promising a **minor, incremental, and modest** change to how things are done in [PLACENAME] [state/city] government, or a **major, sweeping, and drastic** change in how things are done in [PLACENAME] [state/city] government? (1 = *Incremental* to 7 = *Sweeping*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(change,na.rm = T),
            sd = sd(change,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change)

m1 <- rstatix::t_test(change ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,change ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```


```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(change,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  ggplot() +
  geom_histogram(aes(x = change), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Cultural issues

What is their approach to cultural issues? Broadly, they may have a more **progressive approach** to cultural issues (pro-choice, minority rights, inclusive immigration) or a more **conservative approach** to cultural issues (pro-life, stronger police, immigration crackdown). (1 = *Progressive* to 7 = *Conservative*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(cult,na.rm = T),
            sd = sd(cult,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult)

m1 <- rstatix::t_test(cult ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,cult ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(cult,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  ggplot() +
  geom_histogram(aes(x = cult), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Economic policy

What is their approach to economic policy? Broadly, they may be supportive of more **redistributive** economic policies (high corporate taxes, stronger unions, welfare funding) or more **free-market** economic policies (low corporate taxes, deregulation, reducing government budget). (1 = *Redistributive* to 7 = *Free Market*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(econ,na.rm = T),
            sd = sd(econ,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ)

m1 <- rstatix::t_test(econ ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,econ ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(econ,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "New Jersey") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  ggplot() +
  geom_histogram(aes(x = econ), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

## Virginia

### Approach to change

For each candidate, would you describe them as promising a **minor, incremental, and modest** change to how things are done in [PLACENAME] [state/city] government, or a **major, sweeping, and drastic** change in how things are done in [PLACENAME] [state/city] government? (1 = *Incremental* to 7 = *Sweeping*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(change,na.rm = T),
            sd = sd(change,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change)

m1 <- rstatix::t_test(change ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,change ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(change,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  ggplot() +
  geom_histogram(aes(x = change), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Cultural issues

What is their approach to cultural issues? Broadly, they may have a more **progressive approach** to cultural issues (pro-choice, minority rights, inclusive immigration) or a more **conservative approach** to cultural issues (pro-life, stronger police, immigration crackdown). (1 = *Progressive* to 7 = *Conservative*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(cult,na.rm = T),
            sd = sd(cult,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult)

m1 <- rstatix::t_test(cult ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,cult ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(cult,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  ggplot() +
  geom_histogram(aes(x = cult), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Economic policy

What is their approach to economic policy? Broadly, they may be supportive of more **redistributive** economic policies (high corporate taxes, stronger unions, welfare funding) or more **free-market** economic policies (low corporate taxes, deregulation, reducing government budget). (1 = *Redistributive* to 7 = *Free Market*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(econ,na.rm = T),
            sd = sd(econ,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ)

m1 <- rstatix::t_test(econ ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,econ ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(econ,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Virginia") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  ggplot() +
  geom_histogram(aes(x = econ), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

## New York City

### Approach to change

For each candidate, would you describe them as promising a **minor, incremental, and modest** change to how things are done in [PLACENAME] [state/city] government, or a **major, sweeping, and drastic** change in how things are done in [PLACENAME] [state/city] government? (1 = *Incremental* to 7 = *Sweeping*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(change,na.rm = T),
            sd = sd(change,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change)

m1 <- rstatix::t_test(change ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,change ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(change,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  ggplot() +
  geom_histogram(aes(x = change), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Cultural issues

What is their approach to cultural issues? Broadly, they may have a more **progressive approach** to cultural issues (pro-choice, minority rights, inclusive immigration) or a more **conservative approach** to cultural issues (pro-life, stronger police, immigration crackdown). (1 = *Progressive* to 7 = *Conservative*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(cult,na.rm = T),
            sd = sd(cult,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult)

m1 <- rstatix::t_test(cult ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,cult ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(cult,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  ggplot() +
  geom_histogram(aes(x = cult), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Economic policy

What is their approach to economic policy? Broadly, they may be supportive of more **redistributive** economic policies (high corporate taxes, stronger unions, welfare funding) or more **free-market** economic policies (low corporate taxes, deregulation, reducing government budget). (1 = *Redistributive* to 7 = *Free Market*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(econ,na.rm = T),
            sd = sd(econ,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ)

m1 <- rstatix::t_test(econ ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,econ ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(econ,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  ggplot() +
  geom_histogram(aes(x = econ), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

## Seattle

### Approach to change

For each candidate, would you describe them as promising a **minor, incremental, and modest** change to how things are done in [PLACENAME] [state/city] government, or a **major, sweeping, and drastic** change in how things are done in [PLACENAME] [state/city] government? (1 = *Incremental* to 7 = *Sweeping*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(change,na.rm = T),
            sd = sd(change,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change)

m1 <- rstatix::t_test(change ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,change ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(change,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  ggplot() +
  geom_histogram(aes(x = change), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Cultural issues

What is their approach to cultural issues? Broadly, they may have a more **progressive approach** to cultural issues (pro-choice, minority rights, inclusive immigration) or a more **conservative approach** to cultural issues (pro-life, stronger police, immigration crackdown). (1 = *Progressive* to 7 = *Conservative*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(cult,na.rm = T),
            sd = sd(cult,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult)

m1 <- rstatix::t_test(cult ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,cult ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(cult,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  ggplot() +
  geom_histogram(aes(x = cult), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Economic policy

What is their approach to economic policy? Broadly, they may be supportive of more **redistributive** economic policies (high corporate taxes, stronger unions, welfare funding) or more **free-market** economic policies (low corporate taxes, deregulation, reducing government budget). (1 = *Redistributive* to 7 = *Free Market*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(econ,na.rm = T),
            sd = sd(econ,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ)

m1 <- rstatix::t_test(econ ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,econ ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(econ,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  ggplot() +
  geom_histogram(aes(x = econ), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

## Minneapolis

### Approach to change

For each candidate, would you describe them as promising a **minor, incremental, and modest** change to how things are done in [PLACENAME] [state/city] government, or a **major, sweeping, and drastic** change in how things are done in [PLACENAME] [state/city] government? (1 = *Incremental* to 7 = *Sweeping*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(change,na.rm = T),
            sd = sd(change,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change)

m1 <- rstatix::t_test(change ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,change ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(change,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  ggplot() +
  geom_histogram(aes(x = change), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Cultural issues

What is their approach to cultural issues? Broadly, they may have a more **progressive approach** to cultural issues (pro-choice, minority rights, inclusive immigration) or a more **conservative approach** to cultural issues (pro-life, stronger police, immigration crackdown). (1 = *Progressive* to 7 = *Conservative*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(cult,na.rm = T),
            sd = sd(cult,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult)

m1 <- rstatix::t_test(cult ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,cult ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(cult,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  ggplot() +
  geom_histogram(aes(x = cult), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Economic policy

What is their approach to economic policy? Broadly, they may be supportive of more **redistributive** economic policies (high corporate taxes, stronger unions, welfare funding) or more **free-market** economic policies (low corporate taxes, deregulation, reducing government budget). (1 = *Redistributive* to 7 = *Free Market*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(econ,na.rm = T),
            sd = sd(econ,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ)

m1 <- rstatix::t_test(econ ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,econ ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(econ,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  ggplot() +
  geom_histogram(aes(x = econ), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

## Cleveland

### Approach to change

For each candidate, would you describe them as promising a **minor, incremental, and modest** change to how things are done in [PLACENAME] [state/city] government, or a **major, sweeping, and drastic** change in how things are done in [PLACENAME] [state/city] government? (1 = *Incremental* to 7 = *Sweeping*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(change,na.rm = T),
            sd = sd(change,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change)

m1 <- rstatix::t_test(change ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,change ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(change,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_change,cand2_change) %>% 
  pivot_longer(-c(PID,cand1_change,cand2_change),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(change = ifelse(names == "CAND_1",cand1_change,cand2_change)) %>% 
  select(PID,candidate,change) %>% 
  ggplot() +
  geom_histogram(aes(x = change), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Cultural issues

What is their approach to cultural issues? Broadly, they may have a more **progressive approach** to cultural issues (pro-choice, minority rights, inclusive immigration) or a more **conservative approach** to cultural issues (pro-life, stronger police, immigration crackdown). (1 = *Progressive* to 7 = *Conservative*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(cult,na.rm = T),
            sd = sd(cult,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult)

m1 <- rstatix::t_test(cult ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,cult ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(cult,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_cult,cand2_cult) %>% 
  pivot_longer(-c(PID,cand1_cult,cand2_cult),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(cult = ifelse(names == "CAND_1",cand1_cult,cand2_cult)) %>% 
  select(PID,candidate,cult) %>% 
  ggplot() +
  geom_histogram(aes(x = cult), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

### Economic policy

What is their approach to economic policy? Broadly, they may be supportive of more **redistributive** economic policies (high corporate taxes, stronger unions, welfare funding) or more **free-market** economic policies (low corporate taxes, deregulation, reducing government budget). (1 = *Redistributive* to 7 = *Free Market*)

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(n = n(),
            mean = mean(econ,na.rm = T),
            sd = sd(econ,na.rm = T)) %>% 
  ungroup() %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,echo=TRUE,results='asis',warning=FALSE}
formodel <- df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ)

m1 <- rstatix::t_test(econ ~ candidate,data = formodel,paired = T,detailed = T)
m2 <- rstatix::cohens_d(formodel,econ ~ candidate,paired = T)

d = round(m2$effsize,2)

m1 %>% 
  select(statistic,df,p,conf.low,conf.high) %>% 
  mutate(d = d) %>% 
    kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

```{r,fig.align='left',echo=TRUE,warning=FALSE,fig.dim=c(3,3)}
means <- df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  group_by(candidate) %>% 
  summarise(score = mean(econ,na.rm = T)) %>% 
  ungroup()

df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  select(PID,CAND_1:CAND_2,cand1_econ,cand2_econ) %>% 
  pivot_longer(-c(PID,cand1_econ,cand2_econ),
               names_to = "names",
               values_to = "candidate") %>% 
  mutate(econ = ifelse(names == "CAND_1",cand1_econ,cand2_econ)) %>% 
  select(PID,candidate,econ) %>% 
  ggplot() +
  geom_histogram(aes(x = econ), 
                 fill = "lightblue",
                 color = NA,
                 binwidth = 1) +
  scale_x_continuous(limits = c(0,8),
                     breaks = seq(1,7,1)) +
  geom_vline(data = means,mapping = aes(xintercept = score),
             color = "black",
             linetype = "dashed",
             size = 1.1) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.ticks = element_blank(),
        axis.line = element_line(color = "grey66"),
        axis.text.y = element_text(color = "black"),
        axis.text.x = element_text(color = "black",
                                   face = "bold")) +
  facet_wrap(~candidate,nrow = 2)
```

# Voting intentions

## New Jersey

### Turnout

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(STATE == "New Jersey") %>% 
  group_by(vote_turnout) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Who

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(STATE == "New Jersey") %>% 
  group_by(vote_who) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Virginia

### Turnout

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(STATE == "Virginia") %>% 
  group_by(vote_turnout) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Who

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(STATE == "Virginia") %>% 
  group_by(vote_who) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## New York City

### Turnout

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  group_by(vote_turnout) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Who

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "New York City") %>% 
  group_by(vote_who) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Seattle

### Turnout

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  group_by(vote_turnout) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Who

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Seattle") %>% 
  group_by(vote_who) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Minneapolis

### Turnout

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  group_by(vote_turnout) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Who

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Minneapolis") %>% 
  group_by(vote_who) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

## Cleveland

### Turnout

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  group_by(vote_turnout) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

### Who

```{r,echo=TRUE,results='asis',warning=FALSE}
df_lebe_elg %>% 
  filter(PLACENAME == "Cleveland") %>% 
  group_by(vote_who) %>% 
  summarise(N = n()) %>% 
  ungroup() %>% 
  mutate(Perc = round(100*(N/sum(N)),2)) %>% 
  ungroup() %>% 
  arrange(desc(N)) %>% 
  kbl() %>% 
  kable_styling(bootstrap_options = "hover",
                full_width = F,
                position = "left")
```

