---
title: "lebe_oct25b_preprocess"
output: html_document
---

```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(httr)
library(readr)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/left-behind/main/study-oct25b/data/"

df_deid  <- readr::read_csv(paste0(repo_url,"df_raw_deid.csv"), show_col_types = FALSE)

```

remove ineligible participants (including those who got through the Connect filters but were routed out after indicating where they live)

```{r}
#keep only those who finished
df_lebe <- df_deid %>% 
  filter(Finished == 1) %>% 
  filter(Progress == 100) %>% 
  filter(ELIGIBLE == 1)
```

Put NA's where necessary

```{r}
df_lebe <- df_lebe %>% 
  mutate(income = ifelse(income == "Prefer not to answer",NA,income))
```

define income and edu as factors

```{r}
df_lebe <- df_lebe %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")),
         income_num = as.numeric(income),
         edu_num = as.numeric(edu))
```

fix race

```{r}
df_lebe <- df_lebe %>% 
  mutate_at(vars(race_1:race_8),function(x){as.character(x)}) %>% 
  mutate_at(vars(race_1:race_8),function(x){replace_na(x,"")}) %>% 
  mutate(race_num_1 = ifelse(race_1 != "",1,0),
         race_num_2 = ifelse(race_2 != "",1,0),
         race_num_3 = ifelse(race_3 != "",1,0),
         race_num_4 = ifelse(race_4 != "",1,0),
         race_num_5 = ifelse(race_5 != "",1,0),
         race_num_6 = ifelse(race_6 != "",1,0),
         race_num_7 = ifelse(race_7 != "",1,0),
         race_num_8 = ifelse(race_8 != "",1,0),
         race_total = race_num_1 + race_num_2 + race_num_3 + race_num_4 + race_num_5 + race_num_6 + race_num_7 + race_num_8,
         race = ifelse(race_total > 1,"multiracial",paste0(race_1,race_2,race_3,race_4,race_5,race_6,race_7,race_8)),
         race = ifelse(race == "",NA,race)) %>% 
  mutate(white_bin = ifelse(race == "White",1,0))
```

gender

```{r}
df_lebe <- df_lebe %>% 
  mutate(man_bin = ifelse(gender == "man",1,0))
```

party 

```{r}
df_lebe <- df_lebe %>% 
  mutate(rep_bin = ifelse(party_gen == "Republican",1,0),
         dem_bin = ifelse(party_gen == "Democrat",1,0),
         ind_bin = ifelse(party_gen == "Independent",1,0))
```

combine some vars

```{r}
df_lebe <- df_lebe %>% 
  mutate(vote_who = case_when(vote_turnout == "Yes" & vote_who_y == "${e://Field/CAND_1}" ~ CAND_1,
                              vote_turnout == "Yes" & vote_who_y == "${e://Field/CAND_2}" ~ CAND_2,
                              vote_turnout == "Yes" & vote_who_y == "Other" ~ vote_who_y_3_TEXT,
                              vote_turnout == "Yes" & vote_who_y_nyc == "${e://Field/CAND_1}" ~ CAND_1,
                              vote_turnout == "Yes" & vote_who_y_nyc == "${e://Field/CAND_2}" ~ CAND_2,
                              vote_turnout == "Yes" & vote_who_y_nyc == "Curtis Sliwa" ~ "Curtis Sliwa",
                              vote_turnout == "Yes" & vote_who_y_nyc == "Other" ~ vote_who_y_nyc_8_TEXT,
                              vote_turnout != "Yes" & vote_who_n == "${e://Field/CAND_1}" ~ CAND_1,
                              vote_turnout != "Yes" & vote_who_n == "${e://Field/CAND_2}" ~ CAND_2,
                              vote_turnout != "Yes" & vote_who_n == "Other" ~ vote_who_n_3_TEXT,
                              vote_turnout != "Yes" & vote_who_n_nyc == "${e://Field/CAND_1}" ~ CAND_1,
                              vote_turnout != "Yes" & vote_who_n_nyc == "${e://Field/CAND_2}" ~ CAND_2,
                              vote_turnout != "Yes" & vote_who_n_nyc == "Curtis Sliwa" ~ "Curtis Sliwa",
                              vote_turnout != "Yes" & vote_who_n_nyc == "Other" ~ vote_who_n_nyc_6_TEXT,
                              .default = NA))
```

rename some vars

```{r}
df_lebe <- df_lebe %>% 
   rename(lebe_cont = lebe_cont_1)
         
```

reverse-score items

```{r}
# df_lebe <- df_lebe %>% 
#   mutate()
```

recode items

*note that the following were predetermined as "sweeping change" candidates: "Zohran Mamdani", "Jack Ciattarelli", "Katie Wilson", "Omar Fateh"
*note that the following were predetermined as "incremental change" candidates: "Andrew Cuomo", "Mikie Sherill", "Bruce Harrell", "Jacob Frey"

So, for the primary DV (vote_sweep), i'll mark the sweeping candidates as 1, the incremental candidates as 0, and everyone else as NA.
For exploratory DV's, i'll add (1) vote_other: anyone other than the 2 candidates as 1 and everyone else as 0; (2) vote_sweep_all: sweeping candidates as 1 and everyone else as 0; (3) vote_inc_all: incremental candidates as 1 and everyone else as 0.

```{r}
cands_sweep = c("Zohran Mamdani","Jack Ciattarelli","Katie Wilson","Omar Fateh")
cands_inc = c("Andrew Cuomo","Mikie Sherill","Bruce Harrell","Jacob Frey")

df_lebe <- df_lebe %>% 
  mutate(party_followup = case_when(party_gen == "Democrat" ~ paste0("Democrat | ",party_dem),
                                    party_gen == "Republican" ~ paste0("Republican | ",party_rep),
                                    party_gen == "Independent" |
                                      party_gen == "No preference" |
                                      party_gen == "Other party" ~ paste0("Independent | ",party_ind),
                                    .default = NA),
         party_id = case_when(party_followup == "Democrat | Not very strong" |
                                party_followup == "Democrat | Strong" |
                                party_followup == "Independent | Closer to Democratic" ~ "Dem",
                              party_followup == "Republican | Not very strong" |
                                party_followup == "Republican | Strong" |
                                party_followup == "Independent | Closer to Republican" ~ "Rep",
                              party_followup == "Independent | Neither" ~ "Ind",
                              .default = NA)) %>% 
  mutate(vote_sweep = case_when(vote_who %in% cands_sweep ~ 1,
                                vote_who %in% cands_inc ~ 0,
                                .default = NA),
         vote_sweep_all = case_when(vote_who %in% cands_sweep ~ 1,
                                    .default = 0),
         vote_other = case_when(!(vote_who %in% c(cands_sweep,cands_inc)) ~ 1,
                                .default = 0),
         vote_inc_all = case_when(vote_who %in% cands_inc ~ 1,
                                  .default = 0))
```

mean scores

```{r}
df_lebe <- df_lebe %>%
  rowwise() %>%
  mutate(cand1_rightwing = mean(c(cand1_cult,cand1_econ)),
         cand2_rightwing = mean(c(cand2_cult,cand2_econ))) %>%
  ungroup()
```


checks

*note that the first 35 participants didn't see the attention check because of a data collection error. I'll mark those as pass. In fact, anyone with anything other than 14285733 is not a bot, so i'll just check for that number.

```{r}
df_lebe <- df_lebe %>% 
  mutate(is_elg = ifelse(is.na(check_2),1,
                         ifelse(check_2 != "14285733",1,0)))
```

take only necessary variables

```{r}
df_lebe <- df_lebe %>% 
  dplyr::select(PID,
                STATE:COUNTY,
                CAND_1:PLACENAME,
                lebe_cont,
                vote_sweep:vote_inc_all,
                cand1_change,
                cand2_change,
                cand1_rightwing,
                cand2_rightwing,
                cand1_cult:cand2_econ,
                vote_turnout,
                vote_who,
                ideo,
                party_gen,
                party_dem,
                party_rep,
                party_ind,
                party_followup,
                party_id,
                is_elg,
                age,
                gender,
                race,
                edu,
                income,
                income_num,
                edu_num,
                white_bin:ind_bin,
                feedback)
```

write csv

```{r}
write.csv(df_lebe,"~/Google Drive/My Drive/left behind/left behind - github/left-behind/study-oct25b/data/df_lebe.csv",row.names = F)
write.csv(df_lebe %>% filter(is_elg == 1),"~/Google Drive/My Drive/left behind/left behind - github/left-behind/study-oct25b/data/df_lebe_elg.csv",row.names = F)
```

