---
title: "lebe_oct25_preprocess"
output: html_document
---

```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(httr)
library(readr)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/left-behind/main/study-oct25/data/"

df_deid  <- readr::read_csv(paste0(repo_url,"df_raw_deid.csv"), show_col_types = FALSE)

```

remove ineligible participants

```{r}
#keep only those who finished
df_lebe <- df_deid %>% 
  filter(Finished == 1) %>% 
  filter(Progress == 100)
```

Put NA's where necessary

```{r}
df_lebe <- df_lebe %>% 
  mutate(income = ifelse(income == "Prefer not to answer",NA,income))
```

define income and edu as factors

```{r}
df_lebe <- df_lebe %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")),
         income_num = as.numeric(income),
         edu_num = as.numeric(edu))
```

fix race

```{r}
df_lebe <- df_lebe %>% 
  mutate_at(vars(race_1:race_8),function(x){as.character(x)}) %>% 
  mutate_at(vars(race_1:race_8),function(x){replace_na(x,"")}) %>% 
  mutate(race_num_1 = ifelse(race_1 != "",1,0),
         race_num_2 = ifelse(race_2 != "",1,0),
         race_num_3 = ifelse(race_3 != "",1,0),
         race_num_4 = ifelse(race_4 != "",1,0),
         race_num_5 = ifelse(race_5 != "",1,0),
         race_num_6 = ifelse(race_6 != "",1,0),
         race_num_7 = ifelse(race_7 != "",1,0),
         race_num_8 = ifelse(race_8 != "",1,0),
         race_num = race_num_1 + race_num_2 + race_num_3 + race_num_4 + race_num_5 + race_num_6 + race_num_7 + race_num_8,
         race = ifelse(race_num > 1,"multiracial",paste0(race_1,race_2,race_3,race_4,race_5,race_6,race_7,race_8)),
         race = ifelse(race == "",NA,race)) %>% 
  mutate(white_bin = ifelse(race == "White",1,0))
```

gender

```{r}
df_lebe <- df_lebe %>% 
  mutate(man_bin = ifelse(gender == "man",1,0))
```

party 

```{r}
df_lebe <- df_lebe %>% 
  mutate(rep_bin = ifelse(party_gen == "Republican",1,0),
         dem_bin = ifelse(party_gen == "Democrat",1,0),
         ind_bin = ifelse(party_gen == "Independent",1,0))
```

rename some vars

```{r}
df_lebe <- df_lebe %>% 
  rename(lebe_cont = lebe_cont_1,
         cand_exp = elect_exp,
         cand_change = elect_change,
         cand_econ = elect_econ,
         cand_cult = elect_cult,
         lebecool_self = mds_self,
         lebecool_white = mds_white,
         lebecool_black = mds_black,
         lebecool_asian = mds_asian,
         lebecool_latino = mds_latino)
         
         
```

reverse-score items

```{r}
df_lebe <- df_lebe %>% 
  mutate(cand_change_R = 8 - cand_change,
         mob_1R = 8 - mob_1,
         mob_3R = 8 - mob_3,
         mob_7R = 8 - mob_7,
         mob_8R = 8 - mob_8,
         soccon_4R = 8 - soccon_4)
```

recode items

```{r}
df_lebe <- df_lebe %>% 
  mutate(party_followup = case_when(party_gen == "Democrat" ~ paste0("Democrat | ",party_dem),
                                    party_gen == "Republican" ~ paste0("Republican | ",party_rep),
                                    party_gen == "Independent" |
                                      party_gen == "No preference" |
                                      party_gen == "Other party" ~ paste0("Independent | ",party_ind),
                                    .default = NA))
```

mean scores

```{r}
df_lebe <- df_lebe %>% 
  rowwise() %>% 
  mutate(cand_rightwing = mean(c(cand_econ,
                                 cand_cult),na.rm = T),
         mob = mean(c(mob_1R,
                      mob_2,
                      mob_3R,
                      mob_4,
                      mob_5,
                      mob_6,
                      mob_7R,
                      mob_8R),na.rm = T),
         soccon = mean(c(soccon_1,
                         soccon_2,
                         soccon_3,
                         soccon_4R,
                         soccon_5),na.rm = T),
         lonely = sum(c(lonely_1,
                         lonely_2,
                         lonely_3),na.rm = T)) %>% 
  ungroup()
```

cooley measure

The did LPA (latent profile analysis) to classify each participant as one of three profiles (second place; third place; last place). Their paper only had non-hispanic whites, so we should probably (at least at first), limit our analysis to just non-hispanic whites.

```{r}
library(tidyLPA)
library(purrr)
library(tibble)

# ---- 0) Your data ----
# df must have five numeric columns: self, white, black, asian, latinx (0–100 scale is fine)
# Replace these names below if yours differ.
indicators <- c("lebecool_self", "lebecool_white", "lebecool_black", "lebecool_asian", "lebecool_latino")

df_raw <- df_lebe %>% filter(race == "White")
df <- df_raw %>%
  select(any_of(indicators)) %>%
  tidyr::drop_na()              # they listwise-deleted missing on the status measure

# ---- 1) Fit 1–5 class models with Model 1 (equal variances, zero covariances) ----
# Many random starts to reduce local maxima
fit_list <- estimate_profiles(
  df,
  1:5,
  models = 1,                   # Model 1 = equal variances, covariances fixed to 0 (diagonal)
  variances = "equal",
  covariances = "zero",
  starts = 200,                 # random starts (increase if needed)
  nrep = 20                     # # of best solutions to keep improving
)

# ---- 2) Build a robust fit table without compare_solutions() ----
fits <- map_dfr(seq_along(fit_list), function(i) {
  mod <- fit_list[[i]]

  # Coerce get_fit() to a named list we can index safely
  fi_raw <- get_fit(mod)
  fi_list <-
    if (is.data.frame(fi_raw)) {
      as.list(fi_raw[1, , drop = TRUE])
    } else if (is.list(fi_raw)) {
      fi_raw
    } else {
      as.list(fi_raw)
    }

  # helper: pull a numeric, or NA if absent
  getv <- function(nm) {
    v <- fi_list[[nm]]
    if (is.null(v)) return(NA_real_)
    suppressWarnings(as.numeric(v)[1])
  }

  # class sizes -> smallest %
  cl <- get_data(mod) %>% count(Class, name = "n")
  smallest_pct <- if (nrow(cl)) min(cl$n / sum(cl$n)) else NA_real_

  tibble(
    classes      = {
      k <- getv("Classes"); 
      if (is.na(k)) i else as.integer(k)
    },
    logLik       = getv("LogLik"),
    AIC          = getv("AIC"),
    BIC          = getv("BIC"),
    SABIC        = getv("SABIC"),
    Entropy      = getv("Entropy"),
    smallest_pct = smallest_pct
  )
}) %>%
  arrange(classes)

print(fits)


# Heuristics from the paper:
# - prefer lower AIC/BIC/SABIC
# - entropy closer to 1; they were ~.80–.83
# - avoid solutions with any class < .10 of sample

# ---- 3) Select your best solution (likely 3 classes if it mirrors the paper) ----
best_k  <- if (any(fits$classes == 3)) 3 else fits$classes[which.max(fits$Entropy)]
best_fit <- fit_list[[as.integer(best_k)]]

# Examine indicator means by class (mirrors their Tables 3–4)
class_means <- get_estimates(best_fit, what = "means")
print(class_means)

# ---- 4) Export modal class membership (primary predictor) ----
classified <- get_data(best_fit) %>%    # original rows + Class + posterior probs
  rename(lpa_class = Class)

# Optional: entropy-at-person level (classification certainty)
# tidyLPA returns posteriors; you can compute per-person entropy if desired.

# ---- 5) Merge back to your full dataset for downstream models ----
df_with_class <- df_raw %>%
  mutate(.row_id = dplyr::row_number()) %>%
  left_join(classified %>% mutate(.row_id = dplyr::row_number()) %>% select(.row_id, lpa_class), by = ".row_id") %>%
  select(-.row_id)

# --- 0) class means & quick inspection ---
class_means <- classified %>%
  group_by(lpa_class) %>%
  summarise(across(all_of(indicators), ~ mean(.x, na.rm = TRUE)), .groups = "drop")

print(class_means)

inspect <- class_means %>%
  pivot_longer(-lpa_class, names_to = "group", values_to = "mean") %>%
  group_by(lpa_class) %>%
  arrange(desc(mean), .by_group = TRUE) %>%
  mutate(rank_desc = row_number()) %>%
  ungroup()

inspect %>% arrange(lpa_class, rank_desc) %>% print(n = 25)

# --- 1) tolerant rule-based labeling (sweeps eps until it can decide) ---
label_with_eps <- function(df_means, eps = 1.0) {
  df_means %>%
    dplyr::rowwise() %>%
    dplyr::mutate(
      s = lebecool_self,
      w = lebecool_white,
      a = lebecool_asian,
      b = lebecool_black,
      l = lebecool_latino,

      # tolerant comparisons (no function objects created)
      last_place  = (s + eps < w) & (s + eps < a) & (s + eps < b) & (s + eps < l),
      third_place = (s + eps < w) & (s + eps < a) & (s >= b - eps) & (s >= l - eps),
      second_place= (s + eps < w) & (s > a + eps) & (s > b + eps) & (s > l + eps),

      label = dplyr::case_when(
        last_place   ~ "Last Place",
        third_place  ~ "Third Place",
        second_place ~ "Second Place",
        TRUE         ~ "Unclear"
      )
    ) %>%
    dplyr::ungroup() %>%
    dplyr::select(lpa_class, label)
}

# Try a small grid of eps to resolve near-ties
label_df <- label_with_eps(class_means, eps = 1)  # try eps = 1, 2, or 3
print(label_df)

## Different approach

# Inputs assumed:
# - class_means: one row per lpa_class with your five columns:
#   lebecool_self, lebecool_white, lebecool_asian, lebecool_black, lebecool_latino

label_lpa_classes <- function(class_means, eps = 2) {
  cm <- class_means %>%
    mutate(
      s = lebecool_self,
      w = lebecool_white,
      a = lebecool_asian,
      b = lebecool_black,
      l = lebecool_latino,

      # Differences: positive means that group is ABOVE self
      d_w = w - s,
      d_a = a - s,
      d_b = b - s,
      d_l = l - s,

      # Primary rule set with tolerance
      rule_label = case_when(
        # Last Place: self clearly below all four
        (d_w > eps) & (d_a > eps) & (d_b > eps) & (d_l > eps) ~ "Last Place",
        # Third Place: self clearly below White & Asian, and not below Black/Latino
        (d_w >  eps) & (d_a >  eps) & (d_b >= -eps) & (d_l >= -eps) ~ "Third Place",
        # Second Place: self clearly below White only, above the other three
        (d_w >  eps) & (d_a < -eps) & (d_b < -eps) & (d_l < -eps) ~ "Second Place",
        TRUE ~ NA_character_
      )
    )

  # If any NA in rule_label, resolve by prototype distance on the (d_w, d_a, d_b, d_l) vector
  # Prototypes: sign patterns we expect
  protos <- list(
    "Second Place" = c( 1, -1, -1, -1),
    "Third Place"  = c( 1,  1, -1, -1),
    "Last Place"   = c( 1,  1,  1,  1)
  )

  # cosine similarity helper (scale-invariant, good with different magnitudes)
  cos_sim <- function(x, y) {
    x <- as.numeric(x); y <- as.numeric(y)
    nx <- sqrt(sum(x*x)); ny <- sqrt(sum(y*y))
    if (nx == 0 || ny == 0) return(-Inf)
    sum(x*y) / (nx * ny)
  }

  cm_fallback <- cm %>%
    mutate(
      need_fallback = is.na(rule_label),
      # small shrink so tiny diffs don’t explode direction
      v_w = d_w, v_a = d_a, v_b = d_b, v_l = d_l
    ) %>%
    rowwise() %>%
    mutate(
      fallback_label = if (need_fallback) {
        v <- c(v_w, v_a, v_b, v_l)
        # map to best-matching prototype
        sims <- vapply(protos, function(p) cos_sim(v, p), numeric(1))
        names(which.max(sims))
      } else NA_character_
    ) %>%
    ungroup() %>%
    mutate(final_label = coalesce(rule_label, fallback_label)) %>%
    select(lpa_class, final_label,
           lebecool_self, lebecool_white, lebecool_asian, lebecool_black, lebecool_latino,
           d_w, d_a, d_b, d_l)

  cm_fallback
}

# --- Run it ---
resolved <- label_lpa_classes(class_means, eps = 3)   # try eps=2 or 3 on a 0–100 scale
print(resolved %>% select(lpa_class, final_label))



## See if there even is a last place classification

# 1) print means
print(class_means)

# 2) compute diffs: positive means the group is ABOVE self (self is below that group)
cm <- class_means %>%
  mutate(
    s = lebecool_self,
    d_w = lebecool_white  - s,
    d_a = lebecool_asian  - s,
    d_b = lebecool_black  - s,
    d_l = lebecool_latino - s
  ) %>%
  select(lpa_class, starts_with("d_"))

print(cm)

# Quick “last-place presence” check:
# last place should have ALL four diffs > eps
eps <- 2  # try 2–3 for a 0–100 scale
cm %>%
  mutate(is_last_like = (d_w>eps)&(d_a>eps)&(d_b>eps)&(d_l>eps)) %>%
  select(lpa_class, is_last_like) %>%
  print()

# 3) prototype similarity (cosine) to Second / Third / Last
cos_sim <- function(x, y) {
  x <- as.numeric(x); y <- as.numeric(y)
  nx <- sqrt(sum(x*x)); ny <- sqrt(sum(y*y))
  if (nx == 0 || ny == 0) return(-Inf)
  sum(x*y) / (nx * ny)
}

protos <- list(
  "Second Place" = c( 1, -1, -1, -1),  # White>Self>Asian,Black,Latino
  "Third Place"  = c( 1,  1, -1, -1),  # White>Asian>Self>Black,Latino
  "Last Place"   = c( 1,  1,  1,  1)   # everyone above Self
)

sim_table <- cm %>%
  rowwise() %>%
  mutate(
    sim_second = cos_sim(c(d_w,d_a,d_b,d_l), protos[["Second Place"]]),
    sim_third  = cos_sim(c(d_w,d_a,d_b,d_l), protos[["Third Place"]]),
    sim_last   = cos_sim(c(d_w,d_a,d_b,d_l), protos[["Last Place"]]),
    best_label = c("Second Place","Third Place","Last Place")[which.max(c(sim_second, sim_third, sim_last))]
  ) %>%
  ungroup() %>%
  select(lpa_class, sim_second, sim_third, sim_last, best_label)

print(sim_table)


```


alright, i'll approximate something else from the cooley measure, just for the analyses, but it probably won't get the effect because they're only claiming an effect for "last place" participants. alright.

```{r}
temp <- df_lebe %>% 
  select(PID,lebecool_self:lebecool_latino) %>% 
  pivot_longer(-PID,
               values_to = "placement",
               names_to = "dot") %>% 
  group_by(PID) %>% 
  mutate(rankorder = rank(placement)) %>% 
  ungroup() %>% 
  mutate(rankorder = 6 - rankorder) %>% 
  filter(dot == "lebecool_self") %>% 
  select(PID,rankorder) %>% 
  rename(selfplacement = rankorder)

df_lebe <- df_lebe %>% 
  left_join(temp,by= "PID")
```


checks

```{r}
df_lebe <- df_lebe %>% 
  mutate(att_1 = ifelse(check_1 == 5,1,0),
         att_2 = ifelse(check_2 == "14285733",0,1),
         is_elg = ifelse(att_1 == 1 & att_2 == 1,1,0))
```

take only necessary variables

```{r}
df_lebe <- df_lebe %>% 
  dplyr::select(PID,
                lebe_cont,
                cand_rightwing,
                cand_change_R,
                cand_exp:cand_cult,
                mob:selfplacement,
                mob_1R,
                      mob_2,
                      mob_3R,
                      mob_4,
                      mob_5,
                      mob_6,
                      mob_7R,
                      mob_8R,
                soccon_1,
                         soccon_2,
                         soccon_3,
                         soccon_4R,
                         soccon_5,
                lonely_1,
                         lonely_2,
                         lonely_3,
                lebecool_self:lebecool_latino,
                ideo,
                party_gen,
                party_dem,
                party_rep,
                party_ind,
                party_followup,
                att_1,
                att_2,
                is_elg,
                age,
                gender,
                race,
                edu,
                income,
                income_num,
                edu_num,
                white_bin:ind_bin,
                feedback)
```

write csv

```{r}
write.csv(df_lebe,"~/Google Drive/My Drive/left behind/left behind - github/left-behind/study-oct25/data/df_lebe.csv",row.names = F)
```

