---
title: "lebe_oct25_preprocess"
output: html_document
---

```{r,include=FALSE}
detachAllPackages <- function() {

  basic.packages <- c("package:stats","package:graphics","package:grDevices","package:utils","package:datasets","package:methods","package:base")

  package.list <- search()[ifelse(unlist(gregexpr("package:",search()))==1,TRUE,FALSE)]

  package.list <- setdiff(package.list,basic.packages)

  if (length(package.list)>0)  for (package in package.list) detach(package, character.only=TRUE)

}

detachAllPackages()
```

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(httr)
library(readr)

repo_url <- "https://raw.githubusercontent.com/deanbaltiansky/left-behind/main/study-oct25/data/"

df_deid  <- readr::read_csv(paste0(repo_url,"df_raw_deid.csv"), show_col_types = FALSE)

```

remove ineligible participants

```{r}
#keep only those who finished
df_lebe <- df_deid %>% 
  filter(Finished == 1) %>% 
  filter(Progress == 100)
```

Put NA's where necessary

```{r}
df_lebe <- df_lebe %>% 
  mutate(income = ifelse(income == "Prefer not to answer",NA,income))
```

define income and edu as factors

```{r}
df_lebe <- df_lebe %>% 
  mutate(income = factor(income,c("$0-$20,000",
                                  "$20,001-$40,000",
                                  "$40,001-$60,000",
                                  "$60,001-$80,000",
                                  "$80,001-$100,000",
                                  "$100,001-$120,000",
                                  "$120,001-$140,000",
                                  "$140,001-$160,000",
                                  "$160,001-$180,000",
                                  "$180,001-$200,000",
                                  "Over $200,000")),
         edu = factor(edu,c("noHS",
                            "GED",
                            "2yearColl",
                            "4yearColl",
                            "MA",
                            "PHD")),
         income_num = as.numeric(income),
         edu_num = as.numeric(edu))
```

fix race

```{r}
df_lebe <- df_lebe %>% 
  mutate_at(vars(race_1:race_8),function(x){as.character(x)}) %>% 
  mutate_at(vars(race_1:race_8),function(x){replace_na(x,"")}) %>% 
  mutate(race_num_1 = ifelse(race_1 != "",1,0),
         race_num_2 = ifelse(race_2 != "",1,0),
         race_num_3 = ifelse(race_3 != "",1,0),
         race_num_4 = ifelse(race_4 != "",1,0),
         race_num_5 = ifelse(race_5 != "",1,0),
         race_num_6 = ifelse(race_6 != "",1,0),
         race_num_7 = ifelse(race_7 != "",1,0),
         race_num_8 = ifelse(race_8 != "",1,0),
         race_num = race_num_1 + race_num_2 + race_num_3 + race_num_4 + race_num_5 + race_num_6 + race_num_7 + race_num_8,
         race = ifelse(race_num > 1,"multiracial",paste0(race_1,race_2,race_3,race_4,race_5,race_6,race_7,race_8)),
         race = ifelse(race == "",NA,race)) %>% 
  mutate(white_bin = ifelse(race == "White",1,0))
```

gender

```{r}
df_lebe <- df_lebe %>% 
  mutate(man_bin = ifelse(gender == "man",1,0))
```

party 

```{r}
df_lebe <- df_lebe %>% 
  mutate(rep_bin = ifelse(party_gen == "Republican",1,0),
         dem_bin = ifelse(party_gen == "Democrat",1,0),
         ind_bin = ifelse(party_gen == "Independent",1,0))
```

rename some vars

```{r}
df_lebe <- df_lebe %>% 
  rename(lebe_cont = lebe_cont_1,
         cand_exp = elect_exp,
         cand_change = elect_change,
         cand_econ = elect_econ,
         cand_cult = elect_cult,
         lebecool_self = mds_self,
         lebecool_white = mds_white,
         lebecool_black = mds_black,
         lebecool_asian = mds_asian,
         lebecool_latino = mds_latino)
         
         
```

reverse-score items

```{r}
df_lebe <- df_lebe %>% 
  mutate(cand_change_R = 8 - cand_change,
         mob_1R = 8 - mob_1,
         mob_3R = 8 - mob_3,
         mob_7R = 8 - mob_7,
         mob_8R = 8 - mob_8,
         soccon_4R = 8 - soccon_4)
```

recode items

```{r}
df_lebe <- df_lebe %>% 
  mutate(party_followup = case_when(party_gen == "Democrat" ~ paste0("Democrat | ",party_dem),
                                    party_gen == "Republican" ~ paste0("Republican | ",party_rep),
                                    party_gen == "Independent" |
                                      party_gen == "No preference" |
                                      party_gen == "Other party" ~ paste0("Independent | ",party_ind),
                                    .default = NA))
```

mean scores

```{r}
df_lebe <- df_lebe %>% 
  rowwise() %>% 
  mutate(cand_rightwing = mean(c(cand_econ,
                                 cand_cult),na.rm = T),
         mob = mean(c(mob_1R,
                      mob_2,
                      mob_3R,
                      mob_4,
                      mob_5,
                      mob_6,
                      mob_7R,
                      mob_8R),na.rm = T),
         soccon = mean(c(soccon_1,
                         soccon_2,
                         soccon_3,
                         soccon_4R,
                         soccon_5),na.rm = T),
         lonely = sum(c(lonely_1,
                         lonely_2,
                         lonely_3),na.rm = T)) %>% 
  ungroup()
```

cooley measure

alright, i'll approximate something else from the cooley measure, just for the analyses, but it probably won't get the effect because they're only claiming an effect for "last place" participants. alright.

```{r}
temp <- df_lebe %>% 
  select(PID,lebecool_self:lebecool_latino) %>% 
  pivot_longer(-PID,
               values_to = "placement",
               names_to = "dot") %>% 
  group_by(PID) %>% 
  mutate(rankorder = rank(placement)) %>% 
  ungroup() %>% 
  mutate(rankorder = 6 - rankorder) %>% 
  filter(dot == "lebecool_self") %>% 
  select(PID,rankorder) %>% 
  rename(selfplacement = rankorder)

df_lebe <- df_lebe %>% 
  left_join(temp,by= "PID")
```


checks

```{r}
df_lebe <- df_lebe %>% 
  mutate(att_1 = ifelse(check_1 == 5,1,0),
         att_2 = ifelse(check_2 == "14285733",0,1),
         is_elg = ifelse(att_1 == 1 & att_2 == 1,1,0))
```

take only necessary variables

```{r}
df_lebe <- df_lebe %>% 
  dplyr::select(PID,
                lebe_cont,
                cand_rightwing,
                cand_change_R,
                cand_exp:cand_cult,
                mob:selfplacement,
                mob_1R,
                      mob_2,
                      mob_3R,
                      mob_4,
                      mob_5,
                      mob_6,
                      mob_7R,
                      mob_8R,
                soccon_1,
                         soccon_2,
                         soccon_3,
                         soccon_4R,
                         soccon_5,
                lonely_1,
                         lonely_2,
                         lonely_3,
                lebecool_self:lebecool_latino,
                ideo,
                party_gen,
                party_dem,
                party_rep,
                party_ind,
                party_followup,
                att_1,
                att_2,
                is_elg,
                age,
                gender,
                race,
                edu,
                income,
                income_num,
                edu_num,
                white_bin:ind_bin,
                feedback)
```

write csv

```{r}
write.csv(df_lebe,"~/Google Drive/My Drive/left behind/left behind - github/left-behind/study-oct25/data/df_lebe.csv",row.names = F)
write.csv(df_lebe %>% filter(is_elg == 1),"~/Google Drive/My Drive/left behind/left behind - github/left-behind/study-oct25/data/df_lebe_elg.csv",row.names = F)
```

